---
title: "Trivial models for short-term LPG forecasting"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  data_path: "./data/datasets/"
  pattern_datasets: "*.csv"
---

```{r setup, include=FALSE}
library(lpg.short.pred)
knitr::opts_chunk$set(echo = FALSE)
options(knitr.table.format = "html")

# Function which will be used for reading files with data
read_file_function <- readr::read_csv
```

This report presents the prediction errors of different models for different horizons (from 1 to 7 days ahead).

The specified error is **a medium squared error**.

The models used:

* Forecast using the last value of consumption - that is, having the current value of consumption, we forecast that such a value of consumption will also be in the next 7 days.
* Forecast using average consumption over the last 7 days.
* Forecast using median consumption over the last 7 days.
* Linear regression on the last 7 days of consumption, where the y-axis is consumption and the x-axis is an index of the day.
* Linear regression on the last 7 days, where the y-axis is consumption and x-axis is the temperature from preceding days. These models used the forecast temperature.

Green indicates the model error that has reached the lowest value for the horizon.

```{r generate_data, message=FALSE}
r <- naive_models_report(path = params$data_path,
                         pattern = params$pattern_datasets,
                         read_file_function = read_file_function)
```

```{r datasets, echo=FALSE, include=FALSE, results="asis"}
out <- NULL
for(res in r$datasets_models_res) {
  out <- c(out, knitr::knit_child("naive_models_part.Rmd"))
}
```

```{r, echo=FALSE, results="asis"}
cat(paste(out, collapse = '\n'))
```

# Summary of all  datasets

The following are the average error values.

```{r summary}
naive_models_summary(r$summary)
```

# Summary for each month

```{r summary each month, echo=FALSE, include=FALSE, results="asis"}
months_sections <- NULL
for(i in 1:length(r$summary_each_month)) {
  res <- r$summary_each_month[[i]]
  month_name <- names(r$summary_each_month)[i]
  months_sections <- c(months_sections, knitr::knit_child("month_summary.Rmd"))
}
```

```{r, echo=FALSE, results="asis"}
cat(paste(months_sections, collapse = '\n'))
```
